% Marshall Bruner's resume

\documentclass[11pt,a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome5} % cool emojis
\RequirePackage{fontawesome}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{listofitems} % list of command arguments
\usepackage{sectsty} % section formatting
% \usepackage{fontspec}
% \setmonofont{JetBrains Mono}[Contextuals=Alternate]

\usepackage{geometry}
\geometry{
  a4paper,
  left=6mm,
  right=6mm,
  top=10mm,
  bottom=10mm
}

\pagestyle{empty}

% Section formatting
\sectionfont{
    \large
    \sectionrule{0pt}{0pt}{-5pt}{0.5pt}
}

% Name
% Arguments:
% - name
% - address
% - phone number
% - email
% - linkedin
% - github
\newcommand{\name}[7]{
  \begin{center}
    {\Huge \scshape \texttt{#1}} \\ \vspace{1mm}
    #2 \\ \vspace{1mm}
    \small \raisebox{-0.1\height}\faPhone \ \underline{#3} ~
    \href{mailto:#4}{\raisebox{-0.1\height} \faEnvelope \  \underline{#4}} ~
    \href{https://linkedin.com/in/#5}{\raisebox{-0.1\height} \faLinkedinSquare \  \underline{#5}} ~
    \href{https://github.com/#6}{\raisebox{-0.1\height} \faGithub \  \underline{#6}} ~
    \href{https://gitlab.com/#7}{\raisebox{-0.1\height} \faGitlab \  \underline{#7}}
  \end{center}\par
}

% School
% Arguments:
% - school
% - degree
% - GPA
% - start date
% - end date
% - other
% - location
\newcommand{\school}[7]{
  \vspace{-1.5mm}
  % \readlist*\bulletslist{#6}
  \begin{tabularx}{\textwidth}{
    p{10cm}
    >{\raggedleft\arraybackslash}X
  }
    \textbf{#1} & \textbf{#4 \textemdash \ #5} \\
    \textit{#2} \textemdash \  \textbf{\textit{GPA: #3}} & \textit{#7} \\
    \multicolumn{2}{l}{\textit{#6}} \\
    % \begin{itemize}
    %   \foreachitem\bullet\in\bulletslist{\item \bullet\vspace{-0.3cm}}
    % \end{itemize} \\
    % \textit{#6} & \\
  \end{tabularx}
}

% Job
% Arguments:
% - company
% - start date
% - end date
% - location
% - position
% - bullet points (comma-separated list)
\newcommand{\job}[6]{
  \readlist*\bulletslist{#6}
  \vspace{-1.5mm}
  \begin{tabularx}{\textwidth}{
    p{14.5cm}
    >{\raggedleft\arraybackslash}X
    }
    \textbf{#1} & \textbf{#2} \textemdash\  \textbf{#3} \\
    \textit{\underline{#4}} & \textit{#5} \\
    \vspace{-0.7cm}
    \begin{itemize}
      \foreachitem\bullet\in\bulletslist{\item \bullet\vspace{-0.3cm}}
    \end{itemize} \\
  \end{tabularx}
}

% Project
% Arguments:
% - project title
% - start date
% - end date
% - bullet points (comma-separated list)
% - link to project
\newcommand{\project}[5]{
  \readlist*\bulletslist{#4}
  \vspace{-1.5mm}
  \begin{tabularx}{\textwidth}{
    p{14cm}
    >{\raggedleft\arraybackslash}X
    }
    \href{#5}{\underline{\textbf{#1}}} & \textbf{#2} \textemdash\ \textbf{#3} \\
    \vspace{-0.7cm}
    \begin{itemize}
      \foreachitem\bullet\in\bulletslist{\item \bullet \vspace{-0.3cm}}
    \end{itemize}
  \end{tabularx}
}

% Skill
% Arguments:
% - group
% - skills (comma-separated list)
\newcommand{\skill}[2]{
  \begin{tabularx}{\textwidth}{
    X
    }
    \textbf{#1:} #2
  \end{tabularx}
}

\begin{document}
\name{Marshall Bruner}
{Denver, CO}
{+1 970-568-6162}
{brunerm99@gmail.com}
{marshall-bruner}
{brunerm99}
{brunerm99}

\vspace{-0.65cm}

\section*{OBJECTIVE}
\vspace{-0.2cm}
I am pursuing a transition into the Data Science industry.
My motivation has pushed me to learn the necessary tools and apply them to personal projects alongside my demanding job in the aerospace industry.
I believe my expertise as an RF engineer, specifically in the signal processing field, gives me an interesting perspective to contribute to a team.


\vspace{-0.3cm}

\section*{EXPERIENCE}
\job{Ball Aerospace}
{Jun. 2021}
{Present}
{RF Engineer}
{Broomfield, CO}
{
  {Used Python knowledge to create useful plotting and RF analysis tools},
  {Simulated, designed, and tested an RF Front-End PWB at extreme temperatures},
  {Debugged complex, mission-critical RF boards under strict time constraints},
  {Built an embedded webpage used to interact with a phased array antenna},
  {High-power testing of real antenna loads}
}
\job{Colorado State University}
{Jan. 2021}
{May 2022}
{Graduate Research Assistant | Thesis}
{Fort Collins, CO}
{
  {Design, schematic, and layout of a modular, X-band, FMCW drone radar},
  {Signal processing / data visualization for Analog Device’s FMCW Phaser Board},
  {Work for the Phaser Board was presented at IMS 2022 and IEEE-APS 2022},
  {Will personally be presenting work at the International Phased Array Symposium},
  {Built a server to host and display real-time and historical radar data using PostGreSQL, Flask, Python}
}
\job{CHILL Radar Lab}
{May 2020}
{May 2021}
{Lab Assistant}
{Greeley, CO}
{
  {Built a real-time radar display to easily display and animate radar data},
  {Performed characterizations and measurements of radar equipment}
}

\vspace{-0.5cm}

\section*{EDUCATION}
\school{Colorado State University}
{M.S. Electrical Engineering}
{3.9}
{Jan. 2021}
{May 2022}
{Thesis - Design, Deployment, and Cost Considerations for DARMA; A Low-Cost and Lightweight FMCW Radar}
{Fort Collins, CO}
\school{Colorado State University}
{B.S. Electrical Engineering}
{3.47}
{Aug. 2017}
{May 2021}
{}
{Fort Collins, CO}

\vspace{-0.7cm}

\section*{PROJECTS}
\project{5G Electronics Senior Design Project}
{Jun. 2020}
{May 2021}
{{Simulated, assembled, and measured a full 5G receiver system},{Created teaching documentation for a 5G transmitter and receiver for FR1 and FR2 frequency bands},{Experience using FieldFox, EMPro, ADS, SystemVue}}
{https://drive.google.com/file/d/1jnmEm4owg6Irm8_FP4LNQ6NCM40VRgA7/view?usp=sharing}
\project{Fuzzy Logic Clutter Filter}
{Nov. 2020}
{Dec. 2020}
{{Applied the Fuzzy Logic machine learning technique to radar data as a clutter filter}}
{https://drive.google.com/file/d/1ZUYzztMVOXb6Fy5-VPBcrxMdchSZ3y8y/view}
\project{Environment-Mapping Car}
{Nov. 2020}
{Dec. 2020}
{Built and programmed battery-powered car with attached ultrasonic sensor for mobile mapping of the surrounding environment}
{https://drive.google.com/file/d/1jjRZd7_2CnEgP2Gu1lF2XtPDVP_Ej0Gg/view}

\vspace{-0.5cm}

\section*{SKILLS \& ABILITIES}
\vspace{-0.2cm}
\skill{Languages}
{Python, SQL, C, Bash, Matlab, JavaScript, HTML, CSS}
\skill{Technologies / Tools}
{Git, \LaTeX, Linux, Docker, PostGreSQL/TimescaleDB, Flask, Celery (Distributed Tasks)}
\skill{Communication}
{Excellent Technical Communication and Presentation Skills, Experience Presenting PDR/CDRs, Technical Paper/Presentation Formatting, Concise Code Documentation}
% \skill{Design / Simulation Tools}
% {HFSS, KiCad, QucsStudio, LTSpice, Cadence Virtuoso}

\end{document}
